Enhanced Global PTM Discovery (G-PTM-D) with MetaMorpheus

### 2017-11-27 paper.tex
author

\author{Stefan K. Solntsev}
\email{solntsev@wisc.edu}
\author{Michael R. Shortreed}
\author{Brian L. Frey}
\author{Lloyd M. Smith}
\affiliation[UwMadison]
{University of Wisconsin-Madison}

@@

% Enhanced Global PTM Discovery (G-PTM-D) with MetaMorpheus

@@

\end{document}
ven though adducts arising from experimental artifacts are not ultimately interesting to biologists, not including them as an option decreases the total number of identified proteins and PTMs.
The overall identification rate decreases from 220,574 to 217,597 peptide-spectral matches (PSMs), which in turn decreased the number of identified modified peptides by 4\%, see Table~\ref{tab:table3};

\begin{table}[]
\centering
\caption{Effects of Using Different Modification Lists}
\label{tab:table3}
\begin{tabular}{ll|l|l|l}
                      &        & Only UniProt & UniProt+Glycosylations & UniProt+Glycosylations+Adducts\\
\hline
\multirow{2}{*}{PSMs} & Jurkat  & 217597   &  218547 & 220574\\
                      & Mouse    & 170743   &   171432& 174783 
\end{tabular}
\end{table}

\begin{acknowledgement}

The authors thank \ldots
\end{acknowledgement}

\begin{suppinfo}

The following files are available free of charge.
\begin{itemize}
  \item Filename: brief description
  \item Filename: brief description
\end{itemize}

\end{suppinfo}

\end{document}
ent}
ocument}

>>>>

\author{Stefan K. Solntsev}
\author{Michael R. Shortreed}
\author{Brian L. Frey}
\author{Lloyd M. Smith}
\email{smith@chem.wisc.edu}
\affiliation[UwMadison]
{University of Wisconsin-Madison}

@@

@@

\end{document}
